---
title: Code Book
---
#### This code book is to describe the characteristics of the tidy data set *human_activity_data_tidy.txt* generated by *run_analysis.R*

### variables and descriptions

|Variable name  |	Description   |
|:--------------|:----------------|
|activityId  | ID of subjects who performed the activity. Its range is from 1 to 30.
|subjectId	 | ID of activity. Its range is from 1 to 6.|
|timeBodyAccMean-X | average time of Acceleration signal, Body, x-axis, mean |
|timeBodyAccMean-Y | average time of Acceleration signal, Body, y-axis, mean | 
|timeBodyAccMean-Z | average time of Acceleration signal, Body, z-axis, meam |         
|timeBodyAcc-std-X | average time of Acceleration signal, Body, x-axis, std  | 
|timeBodyAcc-std-Y | average time of Acceleration signal, Body, y-axis, std  |  
|timeBodyAcc-std-Z | average time of Acceleration signal, Body, z-axis, std  |  
|timeGravityAccMean-X  | average time of Acceleration signal, Gravity, x-axis, mean |
|timeGravityAccMean-Y  | average time of Acceleration signal, Gravity, y-axis, mean |
|timeGravityAccMean-Z  | average time of Acceleration signal, Gravity, z-axis, mean |
|timeGravityAcc-std-X  | average time of Acceleration signal, Gravity, x-axis, std  |
|timeGravityAcc-std-Y  | average time of Acceleration signal, Gravity, y-axis, std  |
|timeGravityAcc-std-Z  | average time of Acceleration signal, Gravity, z-axis, std  |
|timeBodyAccJerkMean-X | average time of Accelerometer Jerk signal, Body, x-axis, mean |
|timeBodyAccJerkMean-Y | average time of Accelerometer Jerk signal, Body, y-axis, mean |
|timeBodyAccJerkMean-Z | average time of Accelerometer Jerk signal, Body, z-axis, mean |
|timeBodyAccJerk-std-X | average time of Accelerometer Jerk signal, Body, x-axis, std  |
|timeBodyAccJerk-std-Y | average time of Accelerometer Jerk signal, Body, y-axis, std  |
|timeBodyAccJerk-std-Z | average time of Accelerometer Jerk signal, Body, z-axis, std |
|timeBodyGyroMean-X    | average time of Gyroscope signal, Body, x-axis, mean |        
|timeBodyGyroMean-Y    | average time of Gyroscope signal, Body, y-axis, mean |        
|timeBodyGyroMean-Z    | average time of Gyroscope signal, Body, z-axis, mean |        
|timeBodyGyro-std-X    | average time of Gyroscope signal, Body, x-axis, std  |        
|timeBodyGyro-std-Y    | average time of Gyroscope signal, Body, y-axis, std  |        
|timeBodyGyro-std-Z    | average time of Gyroscope signal, Body, z-axis, std  |        
|timeBodyGyroJerkMean-X | average time of Gyroscope Jerk signal, Body, x-axis, mean |       
|timeBodyGyroJerkMean-Y | average time of Gyroscope Jerk signal, Body, y-axis, mean |       
|timeBodyGyroJerkMean-Z  | average time of Gyroscope Jerk signal, Body, z-axis, mean |      
|timeBodyGyroJerk-std-X  | average time of Gyroscope Jerk signal, Body, x-axis, std  |     
|timeBodyGyroJerk-std-Y  | average time of Gyroscope Jerk signal, Body, y-axis, std  |     
|timeBodyGyroJerk-std-Z  | average time of Gyroscope Jerk signal, Body, z-axis, std  |     
|timeBodyAccMagnitudeMean        | average time of Accelerometer signal Magnitude calculated using the Euclidean norm, Body, mean |
|timeBodyAccMagnitudeStdDev      | average time of Accelerometer signal Magnitude calculated using the Euclidean norm, Body, std  |
|timeGravityAccMagnitudeMean     | average time of Accelerometer signal Magnitude calculated using the Euclidean norm, Gravity, mean |
|timeGravityAccMagnitudeStdDev   | average time of Accelerometer signal Magnitude calculated using the Euclidean norm, Gravity, std |
|timeBodyAccJerkMagnitudeMean    | average time of Accelerometer Jerk signal Magnitude calculated using the Euclidean norm, Body, mean |
|timeBodyAccJerkMagnitudeStdDev  | average time of Accelerometer Jerk signal Magnitude calculated using the Euclidean norm, Body, std |
|timeBodyGyroMagnitudeMean       | average time of Gyroscope signal Magnitude calculated using the Euclidean norm, mean |
|timeBodyGyroMagnitudeStdDev     | average time of Gyroscope signal Magnitude calculated using the Euclidean norm, std  |
|timeBodyGyroJerkMagnitudeMean   | average time of Gyroscope Jerk signal Magnitude calculated using the Euclidean norm, Body, mean |
|timeBodyGyroJerkMagnitudeStdDev | average time of Gyroscope Jerk signal Magnitude calculated using the Euclidean norm, std, mean |
|freqBodyAccMean-X     | average frequency of Accelerometer signal, Body, x-axis, mean |   
|freqBodyAccMean-Y     | average frequency of Accelerometer signal, Body, y-axis, mean |         
|freqBodyAccMean-Z     | average frequency of Accelerometer signal, Body, z-axis, mean |         
|freqBodyAcc-std-X     | average frequency of Accelerometer signal, Body, x-axis, std |         
|freqBodyAcc-std-Y     | average frequency of Accelerometer signal, Body, y-axis, std |         
|freqBodyAcc-std-Z     | average frequency of Accelerometer signal, Body, z-axis, std |         
|freqBodyAccJerkMean-X   | average frequency of Accelerometer Jerk signal, Body, x-axis, mean |       
|freqBodyAccJerkMean-Y   | average frequency of Accelerometer Jerk signal, Body, y-axis, mean |       
|freqBodyAccJerkMean-Z   | average frequency of Accelerometer Jerk signal, Body, z-axis, mean |       
|freqBodyAccJerk-std-X   | average frequency of Accelerometer Jerk signal, Body, x-axis, std |       
|freqBodyAccJerk-std-Y   | average frequency of Accelerometer Jerk signal, Body, y-axis, std |       
|freqBodyAccJerk-std-Z   | average frequency of Accelerometer Jerk signal, Body, z-axis, std |       
|freqBodyGyroMean-X      | average frequency of Gyroscope signal, Body, x-axis, mean |      
|freqBodyGyroMean-Y      | average frequency of Gyroscope signal, Body, y-axis, mean |      
|freqBodyGyroMean-Z      | average frequency of Gyroscope signal, Body, z-axis, mean |       
|freqBodyGyro-std-X      | average frequency of Gyroscope signal, Body, x-axis, std |       
|freqBodyGyro-std-Y      | average frequency of Gyroscope signal, Body, y-axis, std |       
|freqBodyGyro-std-Z      | average frequency of Gyroscope signal, Body, z-axis, stds |       
|freqBodyAccMagnitudeMean        | average frequency of Accelerometer signal Magnitude calculated using the Euclidean norm, Body, mean |
|freqBodyAccMagnitudeStdDev      | average frequency of Accelerometer signal Magnitude calculated using the Euclidean norm, Body, std  |
|freaGravityAccMagnitudeMean     | average frequency of Accelerometer signal Magnitude calculated using the Euclidean norm, Gravity, mean |
|freaGravityAccMagnitudeStdDev   | average frequency of Accelerometer signal Magnitude calculated using the Euclidean norm, Gravity, std |
|freaBodyAccJerkMagnitudeMean    | average frequency of Accelerometer Jerk signal Magnitude calculated using the Euclidean norm, Body, mean |
|freaBodyAccJerkMagnitudeStdDev  | average frequency of Accelerometer Jerk signal Magnitude calculated using the Euclidean norm, Body, std |
|freaBodyGyroMagnitudeMean       | average frequency of Gyroscope signal Magnitude calculated using the Euclidean norm, mean |
|freaBodyGyroMagnitudeStdDev     | average frequency of Gyroscope signal Magnitude calculated using the Euclidean norm, std  |
|freaBodyGyroJerkMagnitudeMean   | average frequency of Gyroscope Jerk signal Magnitude calculated using the Euclidean norm, Body, mean |
|freaBodyGyroJerkMagnitudeStdDev | average frequency of Gyroscope Jerk signal Magnitude calculated using the Euclidean norm, std, mean |
|activityType |	Activity names. It's a 6-level factor |



### Dataset structure

Below is the data structure of the tidy data.
The activities have 6 levels:
    1 WALKING
    2 WALKING_UPSTAIRS
    3 WALKING_DOWNSTAIRS
    4 SITTING
    5 STANDING
    6 LAYING

```{r}
str(tidy.df)
```

#### Show a few rows of the dataset
```{r}
head(tidy.df,2)
```

#### Summary of variables

```{r}
summary(tidy.df)
```
